---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MissObs

Note: This package is prepared for practice only. 


The goal of this R package `MissObs` is to count missing values for all columns by group. The function `count_all_missing_by_group` takes the dataframe and returns a data frame or tibble with the number of NAs or missing values within each level of `group`.


## Installation

You can install the development version of `MissObs` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools"
devtools::install_github("stat545ubc-2023/MissObs")
```

## Parameters


## Example

The simple example of what the package function does is provided below.

```{r example}
## Load the package
library(MissObs)

## Load sample data

library(datateachr)

## Calculate count of NAs or missing values for each level of extreme_type category in flow sample data.

missing_values<-count_all_missing_by_group(flow_sample, extreme_type, .groups = "drop")
missing_values

```

In the tibble generated, you can see the function returned the total number or counts if missing values for each groups. For example, the value of the variable **flow** is missing 2 times from the minimum category for value is not missing from the maximum category of the group variable **extreme_type**
